---
title: "Test"
author: "Shang Ju"
date: "September 29, 2016"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(mtcars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Shiny test

```
library(shiny)

ui <- shinyUI(fluidPage(
   
   titlePanel("Slider App"),
   
   sidebarLayout(

      sidebarPanel(
         h1("Move the Slider!"),
         sliderInput("slider2", "Slide Me!",0,100,0)
      ),

      mainPanel(
         h3("Slider Value:"),
         textOutput("text1")
      )
   )
))


server <- shinyServer(function(input, output) {
   
   output$text1 <- renderText(input$slider2 + 10)

})

# Run the application 
shinyApp(ui = ui, server = server)
```

