---
title: "Inferential Data Analysis on ToothGrowth Data"
author: "Shang Ju"
date: "January 22, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,out.width='100%', message = FALSE)
```

## Load the ToothGrowth Data
```{r load data}
library(datasets)
data(ToothGrowth)
```

## ToothGrowth Dataset Overview

The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, (orange juice or ascorbic acid (a form of vitamin C and coded as VC).

## Summary
```{r Summary}
summary(ToothGrowth)
```

## Exploratory Data Analysis
```{r No. Observations}
table(ToothGrowth$supp,ToothGrowth$dose)
```

The dataset is comprised of 60 observations evenly distributed into 6 groups (2 supplements * 3 dose amount)

```{r EDA}
library(ggplot2)
ggplot(data = ToothGrowth,aes(x=dose,y=len)) +
    facet_grid(.~supp) +
    geom_point()
```

From the graph we see that the more dose used, the longer the length of odontoblasts. However, the effectiveness between orange juice (OJ) and Vitamin C (VC) is not significantly different and need further statistical analysis.

## Hypothesis Test 1: Tooth Length Affected by Delivery Method (OJ v.s. VC)

```{r Hypothesis Test 1: supp}
t.test(len~supp, data = ToothGrowth, var.equal=F)
```

Because p-value = 0.06 > 0.05, we can not reject the null hypothesis. So the difference between the effect on tooth growth by delivery methods (orange juice v.s. ascorbic acid) is **not statistically significant**.

## Hypothesis Test 2: Tooth Length Affected by Dose Amount

```{r Hypothesis Test 2: dose 0.5/1}
t.test(len~dose, data = subset(ToothGrowth,dose %in% c(0.5,1)), var.equal=F)
```

p-value 1.3e-7 << 0.05: the effect on tooth growth by dose amount, 0.5 mg/day v.s. 1 mg/day, is significantly different.

```{r Hypothesis Test 2: dose 1/2}
t.test(len~dose, data = subset(ToothGrowth,dose %in% c(1,2)), var.equal=F)
```

p-value 1.9e-5 << 0.05: the effect on tooth growth by dose amount, 1 mg/day v.s. 2 mg/day, is significantly different.


## Conclusions

**Dose amount** affect tooth growth significantly: the higher the amount is (between 0.5 and 2 mg/day), the longer the tooth length.

**Supplement Type (orange juice v.s. ascorbic acid)**, however, does **not** significantly affect tooth growth

The conclusions are based on the assumptions that we take 5% as the significance level and that no other factors are affecting the experiment.
