---
title: "Vehicle Performance by Number of Cylinders"
author: "Shang Ju"
date: "October 12, 2016"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What is this presentation about?

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

We used the build-in dataset "mtcars" in R as example. The goal is to examine the relationship between the vehicles' performance (horsepower, fuel efficiency, acceleration) and numbers of cylinders they have.

## Instructions on the Interactive Plot

- Select the number of cylinders from 4,6,8, and the graph will show you the vehicles accordingly.

- Light blue color represents fast cars and dark blue represents slow cars.

- Horizontal axis shows the fuel efficiency in miles-per-gallon. Vertical axis shows horsepower (how strong the engine is).

## Interactive Plot

```{r eruptions}
library(shiny)
library(ggplot2)

sidebarLayout(
    sidebarPanel(
        selectInput(
            inputId = "cyl", 
            label = p("Number of Cylinders"), 
            choices = sort(unique(mtcars$cyl))
        )
    ),
    
    # Show a plot of the generated distribution
    mainPanel(
        renderPlot({
            mtcars$model <- row.names(mtcars)
                
            # plot of hp and fuel efficiency (mpg)
            ggplot(data = subset(mtcars,cyl == input$cyl),aes(x = mpg, y = hp, label=model)) +
                #geom_point(aes(size = wt,colour = qsec)) +
                #geom_text(aes(label=model),hjust = 0, nudge_x = 0.05, check_overlap = TRUE) +
                #scale_colour_gradient(low = 'cyan2',high = 'blue') +
                #scale_size_area() +
                labs(x = 'Miles per Gallon', y = 'Horsepower', colour = '1/4 mile time',size = 'Weight (1000 lbs)') +
                theme(text = element_text(size=16)) +
                geom_label(aes(fill = qsec,check_overlap = TRUE), colour = "white", fontface = "bold",vjust="inward",hjust="inward") +
                scale_fill_gradient(high = 'blue',low = 'cyan2',name = "1/4 mile time (s)")
        })
    )
)

```

## Conclusions

As you select different values for the # of cylinders, you can see that the more cylinders a vehicle has, the higher horsepower it tends to have.

Also notice that faster cars tend to have high horsepower, but not necessarily high miles-per-gallon. This is because faster cars (sport cars) tend to be lighter in weight, thus require less gasoline to accelerate.

